Discussion Draft

### 2020-04-03 doc/Discussion.rmd
hopefully tiny change
stil small changes

Predictions for this trait are  inconclusive (due to lack of cytology measures from both sexes. We argue that the chromatin structure (and axis length) should be considered as an integral parameter when studying recombination landscape.

We also hypothesize that the sex differences in chromatin structure are closely connected to sex differences  in the interference strength and our results mirror those in [@petkov2007] and follow the prediction that shorter-loop will have stronger interference.

According to the tethered loop model of DSB formation (cite schmenti?), the 'real estate' for COs are the chromatin / DNA loops, the density of whch is conserved in the axis and loop formation (later the SC str), so the number of loops is equvilent to the length of the axis. **The chromosomes are converted to a 2D space (the axis length of a given chromosome is the limited factor for total CO number)**.  Only one of the models COM aligns with our observed results for sexual dimorphism for axis length. **COM** predicts that axis length will be larger in oocytes due to the larger volume.

@@

Logically a negative correlation is expected; increasing the number of crossovers across chromosomes would most logically be done by  more densely spacing crossovers along chromosomes and decreasing interference strength. This pattern has empirical support from the most species [@ottoPaysuer2019] and fits well with  the fundamental relationship between the SC area or axis length, the physical upper limit for the number of crossovers.

>>>>

@@

Logically a negative correlation is expected; increasing the number of crossovers across chromosomes would most logically be done by  more densely spacing crossovers along chromosomes and decreasing interference strength. This pattern has empirical support from the most species [@ottoPaysuer2019] and fits well with  the fundamental relationship between the SC area or axis length, the physical upper limit for the number of crossovers. **although it is not particulary strong in our results** We argue that this is due to difference in scale (genome wide vs single chromosome)
